Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-02 Tex/Old text/fichacatalog.tex
thesis updated text

\thispagestyle{plain}
\begin{center}
%    \Large
%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
%    
%    \vspace{0.4cm}
%    \large
%    Optimal Sizing and Project Validation
%    
%    \vspace{0.4cm}
%    \textbf{Alessandro Trindade}
%    
    \vspace{0.9cm}
    \textbf{Abstract}
\end{center}
verif:
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to validate any kind of system. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated as well, in order to compare performance and soundness. Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.

synthesis:
There exist various methods and tools to size solar photovoltaic systems; however, the tools are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound via symbolic model checking. If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool and real PV systems shows the effectiveness of our approach.

\textit{Keywords}: Formal verification; automated verification; model checking; program synthesis; electrical systems; solar photovoltaic systems

>>>>

\thispagestyle{plain}
\begin{center}
%    \Large
%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
%    
%    \vspace{0.4cm}
%    \large
%    Optimal Sizing and Project Validation
%    
%    \vspace{0.4cm}
%    \textbf{Alessandro Trindade}
%    
    \vspace{0.9cm}
    \textbf{Ficha Catalográfica}
\end{center}
\thispagestyle{plain}
Ficha catalog aqui

### 2019-07-02 Tex/Old text/main.tex
thesis updated text

%\documentclass[10pt,a4paper]{article}
%\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
%Alessandro input: makecell package to permite line break inside tables
\usepackage{makecell}
\usepackage[alf]{abntex2cite}	% citacoes

%\documentclass[12pt,twoside]{report}
%\usepackage[utf8]{inputenc}
%\usepackage{graphicx}
\graphicspath{ {images/} }
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
\fancyfoot{}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[LO,CE]{Chapter \thechapter}
\fancyfoot[CO,RE]{Alessandro Trindade}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

@@

\input{abstract}

%\chapter*{Dedication}
%To mum and dad
%
%\chapter*{Declaration}
%I declare that..
%
\chapter*{Acknowledgements}
I want to thank...

@@

\chapter{Introduction}
\input{chapters/introduction}

@@

\chapter{Experimental Evaluation}
\input{chapters/chapter04}

\chapter{Conclusion and Future Work}
\input{chapters/conclusion}

\appendix
\chapter{Appendix Title}
\input{chapters/appendix}

%\printbibliography
\bibliography{trindadeThesis}{}

>>>>

%\documentclass[10pt,a4paper]{article}
%\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
%Alessandro input: makecell package to permite line break inside tables
\usepackage{makecell}
\usepackage[alf]{abntex2cite}	% citacoes

%\documentclass[12pt,twoside]{report}
%\usepackage[utf8]{inputenc}
%\usepackage{graphicx}
\graphicspath{ {images/} }
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm,bindingoffset=6mm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
%
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

@@

\input{2ndcover}
\thispagestyle{empty}
\pagenumbering{gobble}

\input{fichacatalog}
%\thispagestyle{empty}
\newpage

\input{abstract}
\pagestyle{empty}
%\thispagestyle{empty}

\input{resumo}
%\thispagestyle{empty}

%\chapter*{Dedication}
%To mum and dad
%
%\chapter*{Declaration}
%I declare that..
%
\chapter*{Acknowledgements}
It is not possible to get here without the help of several people. I hope I have not forgotten any and do no wrong.

I would like to thank God (for the gift of life); Solange and Louise (without the patience and support of my family I could not be here); my parents and grandparents; Lucas (for having believed in me and for the patience); the Electricity Department at UFAM (for the support); Professors Feitosa and Barreto from IComp (support and advice); secretary people from IComp (for the support); the financial support from FAPEAM, British Council/Newton Fund and Fundação Amazonas Sustentável; and Coventry University team (Elena, Kojo, and for the opportunity to use field deployed photovoltaic solar systems).

\pagestyle{empty}

@@

\chapter{Introduction}
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
\fancyfoot{}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[CO,CE]{Chapter \thechapter}
\fancyfoot[LO,RE]{A. B. Trindade}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\input{chapters/introduction}

@@

\chapter{Results}
\input{chapters/chapter04}

\chapter{Conclusion and Future Work}
\fancyfoot[CO,CE]{Conclusion and Future Work}
\input{chapters/conclusion}

\appendix
\chapter{Appendix Title}
\fancyfoot[CO,CE]{Appendix}
\input{chapters/appendix}

\fancyfoot[CO,CE]{Bibliography}
%\printbibliography
\bibliography{trindadeThesis}{}
